Fractional Decomposition Trees: A tool for studying mixed-integer-program integrality gaps

### 2018-11-20 IPCO format/FDT.tex
lengend added
refrence added
Adding title, removing orchid and shortening affiliations (no addresses required)

\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{FDT\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Robert Carr\inst{1}\orcidID{} \and
Arash Haddadan\inst{2}\orcidID{} \and
Cynthia Phillips\inst{3}\orcidID{}}
%
\authorrunning{R. Carr, A. Haddadan, C. Phillips}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{University of New Mexico, Albuquerque NM 87131, USA\\
\email{bobcarr@unm.}\\   \and
Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
\email{ahaddada@cmu.edu}\and
Sandia National Laboratories, Albuquerque, NM 87185, USA\\
\email{caphill@sandia.gov}}
%
\maketitle              % typeset the header of the con	tribution
%
\begin{abstract}
We present a new algorithm for finding a feasible solution for a mixed-integer linear program. The algorithm runs in polynomial time and is guaranteed to find a feasible integer solution provided the
integrality gap is bounded. The algorithm is based on convex decomposition of scaled linear-
programming relaxations, so in general it provides a suite of integer solutions. Because of the
relationship between convex decomposition and integrality gaps, this algorithm can be seen as an approximation algorithm. We apply our algorithm our algorithm to a class of 
fractional extreme points for two known problems in combinatorial optimization: the 2-edge-connected spanning subgraph problem and the tree augmentation problem. These computational experiments show that our algorithm can be used as a tool to evaluate the integrality gap of integer programs with their linear relaxation. Finally we provide a stronger characterization of integrality gap for a class of covering problems than that of \cite{goemans}.

@@

>>>>

\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{amsthm}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Fractional Decomposition Trees: A tool for studying mixed-integer-program integrality gaps}
% \thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Robert D. Carr\inst{1} \and
Arash Haddadan\inst{2} \and
Cynthia A. Phillips\inst{3}}

%\author{Robert Carr\inst{1}\orcidID{} \and
%Arash Haddadan\inst{2}\orcidID{} \and
%Cynthia Phillips\inst{3}\orcidID{}}

%
\authorrunning{R. Carr, A. Haddadan, C. Phillips}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
% Shorter institutions
\institute{University of New Mexico, \email{bobcarr@unm.}\\   \and
Carnegie Mellon University, \email{ahaddada@cmu.edu}\and
Sandia National Laboratories, \email{caphill@sandia.gov}}
% Longer version
%\institute{University of New Mexico, Albuquerque NM 87131, USA\\
%\email{bobcarr@unm.}\\   \and
%Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
%\email{ahaddada@cmu.edu}\and
%Sandia National Laboratories, Albuquerque, NM 87185, USA\\
%\email{caphill@sandia.gov}}
%
\maketitle              % typeset the header of the con	tribution
%
\begin{abstract}
We present a new algorithm for finding a feasible solution for a mixed-integer linear program. The algorithm runs in polynomial time and is guaranteed to find a feasible integer solution provided the
integrality gap is bounded. The algorithm is based on convex decomposition of scaled linear-
programming relaxations, so in general it provides a suite of integer solutions. Because of the
relationship between convex decomposition and integrality gaps, this algorithm can be seen as an approximation algorithm. We apply our algorithm our algorithm to a class of 
fractional extreme points for two known problems in combinatorial optimization: the 2-edge-connected spanning subgraph problem and the tree augmentation problem. These computational experiments show that our algorithm can be used as a tool to evaluate the integrality gap of integer programs with their linear relaxation. Finally we provide a stronger characterization of integrality gap for a class of covering problems than that of \cite{goemans}.

@@

	\bibitem[BC11]{Boyd-Carr-2011}
	Sylvia Boyd and Robert Carr.
	\newblock Finding low cost tsp and 2-matching solutions using certain
	half-integer subtour vertices.
	\newblock {\em Discrete Optimization}, 8(4):525--539, 2011.
